Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-06 manuscript.tex
6 updates

In this section, we investigate how the noise of the CCF influences the CCF parameters derived either by a Normal density or a SN density fit. Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot simply vary each point in the CCF with their respective error bar and then recalculate the best SN or Normal density fit, to see how the CCF noise influences N mean RV, SN mean RV, SN median RV, FWHM, SN FWHM, BIS SPAN and $\gamma$. We therefore started from the spectrum, for which we know that each point is totally independent of the others. The standard error on each point of the spectrum is given by the photon noise, which follows a Poisson law and is therefore obtained by taking the square root of the measured flux.

We applied the following method to estimate the error bars on the different parameters derived from the CCF. We first modify the values of all the points in the spectrum given their respective error bars. To do so we added to each point the value randomly drawn from a Gaussian distribution centered on the value of the point and with standard deviation the square root of the flux. We then calculated the CCF from this spectrum using the method presented in \citet{Pepe-2002a}, fitted either a Normal or SN density to this CCF and recorded the different parameters. We redo this process a hundred times, which gives us at the end, a distribution for each CFF parameter. The standard deviations of the obtained distributions is then associated to the standard errors of each CCF parameters.

>>>>

In this section, we investigate how the noise of the CCF influences the CCF parameters derived either by a Normal density or a SN density fit. 
\jessi{Should we note that the CCF noise is from the photon-noise of the spectra?  Is there more to ``noise'' in the previous sentence?}
Because a CCF is obtained from a cross-correlation, each point of a CCF is correlated with the other points. Therefore, we cannot simply vary each point in the CCF by their respective error bars and then recalculate the best SN or Normal density fit to see how the CCF noise influences the estimation of the parameters of interest (i.e., N mean RV, SN mean RV, SN median RV, FWHM, SN FWHM, BIS SPAN and $\gamma$). 
Instead, we go to the individual spectra where the individual measurements can be considered independent fo the other points.
The standard error on each point of a spectrum is given by the photon noise, which follows a Poisson distribution and is therefore estimated by taking the squareroot of the measured flux.

The following method was carried out in order to estimate the error bars on the different parameters derived from the CCF. 
We first modify the values of all the points in the spectrum given their respective error bars. To do so we added to each point the value randomly drawn from a Gaussian distribution centered on the value of the point and with standard deviation the square root of the flux. We then calculated the CCF from this spectrum using the method presented in \citet{Pepe-2002a}, fitted either a Normal or SN density to this CCF and recorded the different parameters. We redo this process a hundred times, which gives us at the end, a distribution for each CFF parameter. The standard deviations of the obtained distributions is then associated to the standard errors of each CCF parameters.
